Efficient and Robust Boolean Operations on N Meshes Based on Hybrid Representations

### 2017-01-21 tex/inter.tex
before classification

\label{section:isect}
%In this step, intersections between faces are computed through triangle-triangle intersection test. We adopt M\"{o}ller's algorithm \cite{moller1997fast} on account of its efficiency and simplicity. However, a naive implementation of M\"{o}ller's algorithm can introduce numerical errors and may fail to produce correct results. Therefore, we integrate plane-based geometry to make it exact. In the following, we first introduce our space division strategy to reduce the number of intersection test. Then we make a quick review of M\"{o}ller's algorithm, and discuss the way to embed plane-based geometry. After that, we discuss how to deal with degenerate cases.

In this step, the intersections between faces are determined by a triangle-triangle intersection test. We use  M\"{o}ller's algorithm \cite{moller1997fast} because of its efficiency and simplicity. To ensure exact intersection computation, we integrate P-rep based geometry into the algorithm. In the following, we first introduce our space division strategy to reduce the number of intersection tests. Then introduce our P-rep based intersection algorithm. Lastly, we discuss how to deal with degenerate cases.

@@

%As intersection detection is performed between each pair of faces, localization is necessary for large CSGs to reduce the number of testing pairs. We use the adaptive octree for this purpose. Our implementation is akin to the implementation in Ogayar et al.'s method \cite{ogayar2015deferred}. Intersection between triangle faces and octree nodes are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same mesh, we call it a \emph{normal cell}. Otherwise, it is a \emph{critical cell}, within which the following intersection computation is performed.

As intersection detection is performed between each pair of faces, space division is necessary to reduce the number of pairs to be tested. We use an adaptive octree for this purpose. Our implementation is akin to the implementation of Ogayar et al. \cite{ogayar2015deferred}. The intersections between triangle faces and octree nodes are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types. If all faces that intersect a leaf belong to the same mesh, we regard it as a \emph{normal cell}. Otherwise, it is regarded as a \emph{critical cell}, within which the following intersection computation is performed.

%The difference between our octree and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains. This is because subdividing normal cells benefits only the point-in-polyhedron test \cite{frisken2002simple}, which seldom uses in our method. This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions.

The difference between our octree and that of Ogayar et al. is that we do not subdivide any normal cell, no matter how many faces it contains. Subdividing normal cells is only beneficial for the point-in-polyhedron test \cite{frisken2002simple}, which is seldom used in our method. This simplification saves significant computing time, especially when intersections between primitives are simple, and located in small regions.

@@

We first make a quick review of M\"{o}ller's V-rep based algorithm. Then we introduce our implicit representations of intersections using planes. After that, we discuss how to implement  M\"{o}ller's algorithm using P-rep based geometry.

@@

@@

The non-robustness of this algorithm stems from computing the coordinates of the intersection vertices (the end points of $Seg_1$ and $Seg_2$). Although implementation of this algorithm with arbitrary precision arithmetic produces exact coordinates, it is too costly for boolean operations with large CSGs. We use plane-based geometry to solve this problem, by implicitly representing intersections with planes.

@@

In our method, the intersection with triangle $t$ is stored as $\bm{\mathcal{I}}\colon\{T, \bm{P}_{ext}, \bm{P}_0, \bm{P}_1, \mathcal{N}\}$. This is the plane-based intersection representation (PBI-rep,  see Fig. \ref{fig:pbi}). The first component, $T$, indicates which triangle $\bm{\mathcal{I}}$ lies on.
$\bm{P}_{ext}$ indicates the plane that $\bm{\mathcal{I}}$ lies on. Note that $T$ is not in $\bm{P}_{ext}$. The first two components indicate that  $\bm{\mathcal{I}}$ lies on the line $T \cap \bm{P}_{ext}$.
The two end points of $\bm{\mathcal{I}}$ are $T \cap \bm{P}_{ext}\cap\bm{P}_0$ and $T \cap \bm{P}_{ext}\cap\bm{P}_1$.
The last component, $\mathcal{N}$, represents the neighborhood faces of $\bm{\mathcal{I}}$. $\mathcal{N}$ can be a single face, or a set faces from different input primitives.

@@

For example, two triangle faces, $t_1$ and $t_2$, originating from meshes $M_i$ and $M_j$, respectively, intersect. Two intersections are generated, ${\bm{\mathcal{I}}}_{12}$ on $t_1$ and ${\bm{\mathcal{I}}}_{21}$ on $t_2$.
For ${\bm{\mathcal{I}}}_{12}$, $T = t_1$ and $\bm{P}_{ext}=\bm{p}_{t_2, sp}$. $\bm{P}_0$ and $\bm{P}_1$ are boundary planes of $t_2$, which will be discussed later.
The last component $\mathcal{N}=t_2$ in general situation. Sometimes, ${\bm{\mathcal{I}}}_{12}$ may lie on the edge of $t_2$ (see Fig. \ref{fig:twin}). This is called \emph{edge intersection}. In this situation, the $\mathcal{N}$ is the set of all faces from $M_j$ adjacent to that edge. Edge intersection is discussed in \S\ref{sec:degenerate}.

@@

In the first step, the computation of signed distances involves only the vertices coordinates and the supporting planes of triangles. Therefore, if the early rejections occur, the bounding planes are not needed at all. In addition, according to the conversion method of Campen et al.\cite{campen2010exact}, the supporting plane is represented by four double precision floating point numbers. The precision of first three parameter $L_a$ and the precision of the last parameter $L_d$ hold the relation $L_d = L_a + L + 1$, where $L$ is the precision of coordinates of input vertices. This means we can compute the signed distance exactly within double-precision. With these two facts, our early rejection is as fast as the vertex-based implementation.

If $t_1$ and $t_2$ are not coplanar, $Seg_1$ and $Seg_2$ are computed. The end points are intersections between the supporting plane of one triangle and an edge of the other triangle. By computing the bounding planes, the end points can be implicitly represented by plane triples, $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$, where $\bm{p}^i_{t_1, b}$ is the bounding plane of the related edge.
Fig. \ref{fig:isect} shows all of the possible intersection conditions between $t_1$ and $\bm{p}_{t_2, sp}$. The coplanar situation is discussed in \S \ref{sec:degenerate}.

@@

\subsection{Handling Degenerate Case }
\label{sec:degenerate}

%While two triangles, if intersecting, intersect on a line segment in most situations, they can also intersect on a point or a convex area (coplanar case). Even if the intersection is a line segment, the intersection can be on triangle edges. These degenerate situations prevent us from performing robust boolean operations. In this section, we offer simple but effective way to deal with all these degenerations, which conceals the complexity of intersections and simplifies later processing.

In most situations, two intersecting triangles intersect on a line segment. However, they can also intersect on a point or a convex area (coplanar case). Even if the intersection is a line segment, the intersection can be on an edge. These degenerate situations prevent us from performing robust boolean operations. In this section, we demonstrate a simple but effective way of dealing with all of these degenerations, which conceals the complexity of intersections, and simplifies later processing.

%%%The criterion of whether an intersection help tessellation is by its necessity: if the intersection is not presented, whether some faces from the linked halfedge will cross the boundary of primitives. The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.

\subsubsection{Point intersection}
\label{sec:ipoint}
%If two triangles intersect on a single point (e.g., Fig. \ref{fig:isect}d), the intersection cannot be represented using our four-component description since the line segment collapses into a single point. In these cases, we simply add the intersection point into the related triangles to guarantee correct tessellation. No intersection is introduced.

If two triangles intersect at a single point (such as in Fig. \ref{fig:isect}d) then the intersection cannot be represented using our four-component description, because the line segment collapses into a single point. In these cases, we simply add the intersection point into the related triangles, which guarantees correct tessellation. No further intersections are introduced.

@@

%When intersection line segment lies on the edge of face, we call it \emph{edge intersection}. The space near edge intersection is divided by faces around the intersected edge (typically two faces for a manifold edge), instead of just one face. Therefore, the neighborhood of the related intersection is a set of faces instead of a single one. For example, in Fig. \ref{fig:twin}, the neighborhood of the intersection on $t_1$ is $\{t_2, t^*_2\}$.

When an intersecting line segment lies on the edge of a face, we refer to it as \emph{edge intersection}. The space near the edge intersection is divided by the faces around the intersected edge (typically two faces for a manifold edge), instead of by just one face. Therefore, the neighborhood of the corresponding intersection is a set of faces rather than a single face. For example, in Fig. \ref{fig:twin}, the neighborhood of the intersection on $t_1$ is $\{t_2, t^*_2\}$.

%Another thing needs to be noticed is that there will be repetitive detection of edge intersections. For example, in Fig. \ref{fig:twin}a, the same intersection on $t_1$ will be detected twice because $t_1$ intersect both $t_2$ and $t_2^*$ in exactly the same intersection. We solve this duplication together with other interactions among different intersections in \S\ref{sec:tessellation}. We also call such $t_2$ and $t_2^*$ as \emph{companion triangles} in an edge intersection because they share the same edge intersection. This concept will be referred again in the discussion of coplanar cases.

Edge intersections will be repeatedly detected. For example, in Fig. \ref{fig:twin}a, the same intersection on $t_1$ will be detected twice, because $t_1$ intersects both $t_2$ and $t_2^*$ at the same intersection. We solve this duplication, together with similar interactions between different intersections in \S\ref{sec:tessellation}. We regard $t_2$ and $t_2^*$ as \emph{companion triangles}, because they share the same edge intersection. This concept is referred to again in the discussion of coplanar cases.

>>>>

\label{section:isect}

In this step, the intersections between faces are determined by triangle-triangle intersection tests. We use  M\"{o}ller's algorithm \cite{moller1997fast} because of its efficiency and simplicity. To ensure exact intersection computation, we integrate plane-based geometry into this algorithm. In the following, we first describe our space division algorithm, which reduces the number of intersection tests. Then our plane-based intersection algorithm is introduced. Lastly, we discuss how to deal with degenerate situations.

@@

As intersection detection is performed between each pair of faces, space division is necessary to reduce the number of testing pairs. We use an adaptive octree for this purpose. Our implementation is akin to the implementation of Ogayar et al. \cite{ogayar2015deferred}. The intersections between triangle faces and octree nodes are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types. If all faces that intersect a leaf belong to the same mesh, we regard it as a \emph{normal cell}. Otherwise, it is regarded as a \emph{critical cell}, within which the triangle-triangle intersection tests are performed.

The difference between our octree and that of Ogayar et al. is that we do not subdivide any normal cell, no matter how many faces it contains. Subdividing normal cells is only beneficial for the point-in-polyhedron test \cite{frisken2002simple}, which is seldom used in our method. This simplification saves significant computing time, especially when intersections between primitives are sparse located in small regions.

@@

We first make a quick review of M\"{o}ller's vertex-based algorithm. Then we introduce our implicit representations of intersections using planes. After that, we discuss how to implement M\"{o}ller's algorithm using plane-based geometry.

@@

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{projection}
\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$. $Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$. The intersection between $t_1$ and $t_2$ (yellow line segment) is the overlap of $Seg_1$ and $Seg_2$.}
%Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
\label{fig_projection}
\end{figure}

@@

The non-robustness of this algorithm stems from computing the coordinates of the intersection vertices (the end points of $Seg_1$ and $Seg_2$). Although implementation of this algorithm with arbitrary precision arithmetic produces exact coordinates, it is too costly for boolean evaluations with large CSGs.

@@

In our method, an intersection line segment  $\bm{\mathcal{I}}$ is stored as $\{T, \bm{P}_{ext}, \bm{P}_0, \bm{P}_1, \mathcal{N}\}$. This is the plane-based intersection representation (PBI-rep,  see Fig. \ref{fig:pbi}). The first component, $T$, indicates which triangle $\bm{\mathcal{I}}$ lies on.
$\bm{P}_{ext}$ indicates the plane that $\bm{\mathcal{I}}$ lies on. $T$ should not be in $\bm{P}_{ext}$. Thus the first two components indicate that  $\bm{\mathcal{I}}$ lies on the line $T \cap \bm{P}_{ext}$.
Then two end points of $\bm{\mathcal{I}}$ are $T \cap \bm{P}_{ext}\cap\bm{P}_0$ and $T \cap \bm{P}_{ext}\cap\bm{P}_1$.
The last component, $\mathcal{N}$, represents the neighborhood faces of $\bm{\mathcal{I}}$. $\mathcal{N}$ can be a single face, or a set faces from one or more input primitives.

@@

For example, two triangle faces, $t_1$ and $t_2$, originating from meshes $M_i$ and $M_j$ respectively, intersect. Two intersections are generated, ${\bm{\mathcal{I}}}_{12}$ on $t_1$ and ${\bm{\mathcal{I}}}_{21}$ on $t_2$.
For ${\bm{\mathcal{I}}}_{12}$, $T = t_1$ and $\bm{P}_{ext}=\bm{p}_{t_2, sp}$. $\bm{P}_0$ and $\bm{P}_1$ are boundary planes of $t_2$, which will be discussed later.
The last component $\mathcal{N}=t_2$ in general situation. Sometimes, ${\bm{\mathcal{I}}}_{12}$ may lie on the edge of $t_2$ (see Fig. \ref{fig:twin}). This is called \emph{edge intersection}. In this situation, the $\mathcal{N}$ is the set of all the faces from $M_j$ adjacent to that edge. Edge intersection is discussed in \S\ref{sec:degenerate}.

@@

In the first step, the computation of signed distances involves only the vertices coordinates and the supporting planes of triangles. Therefore, if the early rejections occur, the bounding planes are not needed at all. In addition, according to the conversion method of Campen et al.\cite{campen2010exact}, the supporting plane is represented by four double-precision floating-point numbers. The precisions of the first three parameters and the last parameter are $L_a$ and $L_d$ respectively. They hold the relation $L_d = L_a + L + 1$, where $L$ is the precision of the coordinates of input vertices. This means we can compute the signed distance exactly within double-precision. With these two facts, our early rejection is as fast as the vertex-based implementation.

If $t_1$ and $t_2$ are not coplanar, $Seg_1$ and $Seg_2$ are computed. The end points are intersections between the supporting plane of one triangle and an edge of the other triangle. By computing the bounding planes, the end points can be implicitly represented by plane triples, $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$, where $\bm{p}^i_{t_1, b}$ is the bounding plane of the related edge.
Fig. \ref{fig:isect} shows all of the possible intersection conditions between $t_1$ and $\bm{p}_{t_2, sp}$. The coplanar situation is discussed specifically in \S \ref{sec:degenerate}.

@@

\subsection{Handling Degenerate Situations }
\label{sec:degenerate}

In most situations, intersections between triangles are line segments. However, they can also intersect on a point or a convex area. Even if the intersection is a line segment, the intersection can be on a primitive edge. These degenerate situations prevent us from performing robust boolean operations. In this section, we demonstrate our simple but effective ways of dealing with these degenerations, which conceals the complexity of intersections, and simplifies later processing.

\subsubsection{Point intersection}
\label{sec:ipoint}

If two triangles intersect at a single point (e.g., Fig. \ref{fig:isect}d) then the intersection cannot be represented using our PBI-rep. In this situation, we simply add the intersection point into the related triangles, guaranteeing correct tessellation. No intersection line segment is introduced.

@@

When a triangle intersects with the edge of other triangle, the generated intersection is referred as \emph{edge intersection}. The neighboring faces of the intersection is the set of all the faces that shared the edge rather than a single face. For example, in Fig. \ref{fig:twin}a, the neighboring faces of the intersection on $t_1$ are $t_2$ and $t^*_2$.

An edge intersection will be repeatedly detected. For example, in Fig. \ref{fig:twin}a, the same intersection on $t_1$ will be detected twice, because $t_1$ intersects both $t_2$ and $t_2^*$ at the same line segment. We solve this duplication in tessellation stage (see \S\ref{sec:tessellation}). We regard $t_2$ and $t_2^*$ as \emph{companion} triangles, because they are the neighboring faces of the same edge intersection. This concept will be referred to again in the discussion of coplanar cases.

### 2017-01-21 tex/overview.tex
before classification

In our method, we use V-reps for coarse tests and fast connectivity queries and P-reps for exact predicates. The framework of our method is based on \cite{ogayar2015deferred}, which is a vertex-based method. Plane-based algorithms are embedded into the processing. This embedding is not a simple plane-based implementation of vertex-based algorithms. We develop three efficient algorithms which is optimized under P-reps: triangle-triangle intersection tests, triangle tessellation and polygon classification. These three algorithms are corresponding to the three sources of non-robustness discussed in \S\ref{sec:paradig}. The major difficulty is to avoid any computation under high precision, which means our method is designed to be implemented using only common double-precision floating-point arithmetic. Though BSP-based methods \cite{bernstein2009fast,campen2010exact} also do not use high precision arithmetic, this constrain is harder to satisfy under a vertex-based framework.

@@

\noindent Within the plane $\bm{p}_0$, the point-line orientation is computed by the line parameters and point coordinates under V-reps. Under P-reps, we map this problem to point-plane orientation by picking a plane $\bm{p_l}$ which satisfy three requirements: 1) the line is in $\bm{p_l}$. 2) $\bm{p_l}$ is not parallel with $\bm{p}_0$. 3) $\bm{n}(\bm{p}_0) \times \bm{n}(\bm{p_l})$ has the same orientation as the line.

@@

%There are three steps to our method. The first step is to compute the intersections between each triangle face pair. In the second step, the input meshes are tessellated into intersection-free meshes according to these intersections. Lastly, each face is classified and the final mesh is generated.

Before going into details, we give an overview of our method. While the framework is similar to a V-rep based boolean method, we address the major differences in each stage and briefly explain why these differences are necessary.

@@

In this step, we compute the intersections between pairs of triangles. The triangle-triangle intersection algorithm is largely based on M\"{o}llers algorithm \cite{moller1997fast}. However, the conventional V-rep based implementation of M\"{o}ller's algorithm introduces numerical errors. Our P-rep based intersection algorithm implicitly represents intersections using planes to avoid errors. In addition, we carefully deal with degenerate cases, including point intersections, edge intersections, and coplanar intersections. Furthermore, octree is used to speed up the process. Details are provided in \S\ref{section:isect}.

@@

%Once all intersections between triangles are detected, we need to tessellate the input meshes and construct the intersection-free meshes. In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation. However, for a CSG with more than two meshes, intersections may overlap or intersect with each other, and cannot be used for constraints of CDT directly. In addition, as our intersections are represented by planes, implementation of CDT are complex and inefficient, as most CDT algorithms (e.g. \cite{chew1989constrained}, \cite{de1992line}) is not designed to handle planes and requires explicit coordinates. Therefore, we first perform intersection refinement to resolve intersecting intersections. After that, we construct a graph-like structure suitable for P-rep intersections, called \emph{tess-graph}, to guide the exact tessellation of each face. After all faces are tessellated, we get our intersection-free meshes. Details are shown in \S\ref{sec:tessellation}.

Once all of the intersections between triangles are determined, input meshes are subdivided, so that all intersections occurs on edges and vertices. In many existing methods (e.g., \cite{ogayar2015deferred,zhou2016mesh}), 2D constrained Delaunay triangulation (CDT) \cite{chew1989constrained}\cite{de1992line} is used to implement this stage. In our method, intersections are represented by planes. Therefore, projection is not allowed and the 2D CDT has to be mapped to an equivalent 3D problem. However, a 2D CDT needs to construct edges between arbitrary pair of vertices, whose equivalent 3D operation is to construct new planes which contains arbitrary two vertices. The newly constructed planes require extra precision to represent, and computations with them are slow.

Therefore, we choose to tessellate in a more conservative way that do not add any new edges. As a consequence, the subdivided faces are no more triangles. We first perform intersection refinement to resolve intersections between intersections to make them \emph{regularized}. We then construct a graph-like structure, called a \emph{tess-graph}, to guide the exact tessellation of each face. Details are given in \S\ref{sec:tessellation}.

@@

The purpose of this step is to collect faces that pass the CSG expression from the tessellated meshes to generate the final mesh. However, literally computing the inclusion label vector of each face is unacceptably slow for large CSGs. We utilize the connectivity information to propagate inclusion labels in a flood-filling manner. The seed labels used for flood-filling have to be computed beforehand. Typically, a seed face label is deduced by the label of point on that face. However, the point label can be incorrectly computed without exact arithmetic. We exactly computed face label by a local BSP constructed according to the faces of neighborhoods. Our algorithm does not requires exact arithmetic. Also, the constructed BSP is typically small, which resulting in good performance. Details are given in \S\ref{sec:classification}.

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{projection}
\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$. $Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$. The intersection between $t_1$ and $t_2$ (yellow line segment) is the overlap of $Seg_1$ and $Seg_2$.}
%Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
\label{fig_projection}
\end{figure}

>>>>

In our method, we use V-reps for coarse tests and fast connectivity queries and P-reps for exact predicates. The framework of our method is based on \cite{ogayar2015deferred}, which is a vertex-based method. Plane-based algorithms are embedded into the processing. This embedding is not a simple plane-based implementation of vertex-based algorithms. We develop three efficient algorithms which is optimized under P-reps: triangle-triangle intersection tests, triangle tessellation and polygon classification. These three algorithms are corresponding to the three sources of non-robustness discussed in \S\ref{sec:paradigm}. The major difficulty is to guarantee the efficiency and exactness simultaneously. For this purpose, we avoid any computation under high precision, which means our method is designed to be implemented using only common double-precision floating-point arithmetic.

@@

\noindent Within the plane $\bm{p}_0$, the point-line orientation is computed by the line parameters and point coordinates under V-reps. Under P-reps, we map this problem to point-plane orientation by picking a plane $\bm{p_l}$ which satisfy three requirements: 1) the line is in $\bm{p_l}$; 2) $\bm{p_l}$ is not parallel with $\bm{p}_0$; 3) $\bm{n}(\bm{p}_0) \times \bm{n}(\bm{p_l})$ has the same orientation as the line.

@@

Before going into details, we give an overview of our method. While the framework is similar to vertex-based boolean method, we address the major differences in each stage and briefly explain why these differences are necessary.

@@

We compute the intersections between pairs of triangles. The triangle-triangle intersection algorithm is largely based on M\"{o}ller's algorithm \cite{moller1997fast}. However, the conventional vertex-based implementation of M\"{o}ller's algorithm introduces numerical errors. Our plane-based intersection algorithm implicitly represents intersections using planes to avoid errors. In addition, we carefully deal with all of the degenerate situations, including point intersections, edge intersections, and coplanar intersections. Furthermore, octree is used to speed up the process. Details are provided in \S\ref{section:isect}.

@@

Once all of the intersections between triangles are determined, input meshes are subdivided, so that all intersections occurs on edges and vertices. In many existing methods (e.g., \cite{ogayar2015deferred,zhou2016mesh}), 2D constrained Delaunay triangulation (CDT) \cite{chew1989constrained,de1992line} is used to implement this stage. In our method, intersections are represented by planes. Therefore, projection is not allowed and the 2D CDT has to be mapped to an equivalent 3D problem. However, a 2D CDT needs to construct edges between arbitrary pair of vertices, whose equivalent 3D operation is to construct new planes. The newly constructed planes have to contain arbitrary pair of vertices, thus require extra precision to represent.

To avoid this problem, we choose to tessellate in a more conservative way that do not add any new edges. As a consequence, the subdivided faces are no more triangles but polygons. We first perform intersection refinement to resolve intersections between intersections. We then construct a graph-like structure, called \emph{tess-graph}, to guide the exact tessellation of each face. Details are given in \S\ref{sec:tessellation}.

@@

The purpose of this step is to collect faces that pass the boolean expression from the tessellated meshes to generate the final mesh. However, literally computing the inclusion label vector of each face is unacceptably slow for large CSGs. We utilize the connectivity information to propagate inclusion labels in a flood-filling manner. Typically, the seed face label is deduced by the label of a point on that face. However, the computation of point label can be incorrect without exact arithmetic. We exactly computed face label by a local BSP constructed according to the faces of neighborhoods. Our algorithm does not requires exact arithmetic. Also, the constructed BSP is typically small, which resulting in good performance. Details are given in \S\ref{sec:classification}.

### 2017-01-21 tex/tess.tex
before classification

%So far, intersections are only independent data that store the coordinates and neighbourhood information. To perform tessellation and extract subfaces, we need to organize them to reveal the topology. We use tess-graph for this purpose. A tess-graph is the graph description of the tessellated face topology. For each face to be tessellated, we construct a tess-graph according to the refined intersections. Nodes of tess-graph represent end points of intersections and undirectional connections between nodes represent intersections. The construction of tess-graph is straightforward and the reader will not have problem filling the details.

Intersections are independent data that store coordinates and neighborhood information. To perform tessellation and extract subfaces, we need to organize them to determine topology. We use a tess-graph for this purpose. A tess-graph is the graph description of the tessellated face topology. For each face to be tessellated, we construct a tess-graph from the refined set of intersections. Nodes of the tess-graph represent the end points of intersections, and nondirectional connections between nodes represent intersections. The construction of a tess-graph is straightforward, and readers should be able to determine the details.

%After we have tess-graph, we tessellate face and extract subfaces according to it. This is done by extract valid loops on tess-graph. A valid loop must satisfy two criterions: 1) the direction of loops should be coherent with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order. Each valid loop corresponds to a intersection-free face. After we find out all valid loops on tess-graph, we finish tessellating the corresponding face (see Fig. \ref{fig:cadj}). To facilitate the later process, we also store neighborhood information into the edges of the new faces. The neighborhood information is inherent from the corresponding intersections. When all faces are tessellated, meshes are intersection-free.

After the tess-graph is constructed, we tessellate the face and extract subfaces from it. Subfaces are extracted from valid loops on the tess-graph. A valid loop must satisfy two criteria: 1) the direction of the loop should correspond with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order. Each valid loop corresponds to an intersection-free face. After all of the valid loops are determined from the tess-graph, the corresponding face is tessellated (Fig. \ref{fig:cadj}). To facilitate later processes, we also store neighborhood information in the edges of the new faces. The neighborhood information is determined from the corresponding intersections. When all faces are tessellated, the corresponding meshes are intersection-free.

>>>>

To perform tessellation and extract subfaces, we use tess-graph, which is the graph description of the tessellated face topology. For each intersecting triangle face, we construct a tess-graph according to the refined set of intersections. Nodes of the tess-graph represent the end points of intersections, and connections between nodes represent intersections. The construction of a tess-graph is straightforward, and readers should be able to determine the details.

After the tess-graph is constructed, we extract subfaces by   valid loops. A valid loop is a loop in tess-graph which satisfy two criteria: 1) the direction of the loop should correspond with the face normal, and 2) consecutive connections on the loop should be adjacent by circular order. Each valid loop corresponds to an intersection-free face. After all of the valid loops are determined from the tess-graph, the corresponding face is tessellated (see Fig. \ref{fig:cadj}). To facilitate face classification, we also store neighboring faces in the edges of the new faces. Because the edges have one-to-one correspondence to the connections in tess-graph , and the connections have one-to-one correspondence to the PBI-reps, the neighboring faces of edges is determined from the corresponding PBI-reps.
